The nature that determine an anime show's popularity involves its source material, year of release, episode count, and format it was presented in.

### 2023-04-21 outputs/paper/paper.qmd
- Updated Quarto document - Fixed YAML on data cleaning script file

---
title: The nature that determine an anime show's popularity involves the source material of the adaptation and the years it was released.
author: 
  - Justin Abando
thanks: "Code and data are available at: https://github.com/justabando/malanalysis."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "There are online lists and forums where users can vote on what they believe to be the most popular anime such as MyAnimeList (MAL). However, there are no metrics that can determine why specific anime stand out, and so data was retrieved to determine what factors could be responsible for a show's popularity. It was found that the source material and year of the anime's release were significant in determining how many users of MAL watched the anime. The findings of this paper suggests reasons why a particular anime becomes popular, which can be relevant to those that are new to watching anime or those that want something new to watch as they would gravitate to shows that receive traction by a broader demographic."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

  With a large user base, MAL members can personally rate and review the shows that they watch and catalogue them in their anime lists. While this is useful at the individual level to keep track of their own journey and see the depth and breadth of the shows they watch, it is also useful at the community level. The rating and reviews that are given from individuals are aggregated and averaged using all of the data from other MAL users to give an overall subjective ranking of each show in terms of popularity and rating. It should be noted that a show's ranking is not defined by objective means, but is the majority voice of all the subjective reviews left by the users of the website. With MAL, popularity and rating are both metrics used to sort and determine the top anime based on the reviews and ratings that were given to them by users. While the rating of the show matters for popularity to an extent, a large part of it's score is dependent on the content of the show itself. The rating is dependent on a scale of 1-10, and takes the average score of all the users that have rated the show. Meanwhile, popularity as a ranking metric demonstrates how much exposure the show has gotten and its outreach across as many demographics as possible, and is a ranking that is determined by the amount of users that rated the show regardless if it was positive or not.

@@

  It was found that the source material of the anime that it was adapted into had a significant impact on MAL viewership of anime, as shown with a linear regression model found in @sec-model. Additionally, ___________.

@@

The important variable of note to consider from this list is `members`. This is a quantitative variable that popularity ranking on MAL is completely dependent on. The popularity ranking of an anime is directly affected by how many members an anime has, and so an anime that has the most members would have the #1 popularity ranking. Other than `title`, the rest of the variables will be tested to see if they have any kind of influence on the amount of users that have specific shows on their lists.

@@

##

@@

There are many limitations that are present in this statistical analysis. First, the depth of information is vast as there are many other variables that can be considered when determining the popularity of an anime. Factors from the production side such as the studios that produced the anime, to licensors that release the show on platforms to be watched on are also important for gathering attention to shows. In addition, factors that may give more information about what the show might be about such as the genres and themes may also play an important role as personal appeaal to specific genres may help gravitate MAL users to watch particular shows.

Another consideration that has to be made is in regards to

>>>>

---
title: The nature that determine an anime show's popularity involves its source material, year of release, episode count, and format it was presented in.
author: 
  - Justin Abando
thanks: "Code and data are available at: https://github.com/justabando/malanalysis."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "There are online lists and forums where users can vote on what they believe to be the most popular anime such as MyAnimeList (MAL). However, there are no metrics that can determine why specific anime stand out, and so data was retrieved to determine what factors could be responsible for a show's popularity. It was found that the source material, and year of the anime's release, episode count, and format it was presented in were significant in determining how many users of MAL watched the anime. The findings of this paper suggests reasons why a particular anime becomes popular, which can be relevant to those that are new to watching anime or those that want something new to watch as they would gravitate to shows that receive traction by a broader demographic."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

  With a large user base, MAL members can catalogue the anime they watch in their own personalized lists that they can share with others. In addition, users can rate and review the shows that they watch and catalogue them in their anime lists. While this is useful at the individual level to keep track of their own journey and see the depth and breadth of the shows they watch, it is also useful at the community level. The rating and reviews that are given from individuals are aggregated and averaged using all of the data from other MAL users to give an overall subjective ranking of each show in terms of popularity and rating. It should be noted that a show's ranking is not defined by objective means, but is the majority voice of all the subjective reviews left by the users of the website. With MAL, popularity and rating are both metrics used to sort and determine the top anime based on the reviews and ratings that were given to them by users. While the rating of the show matters for popularity to an extent, a large part of it's score is dependent on the content of the show itself. The rating is dependent on a scale of 1-10, and takes the average score of all the users that have rated the show. Meanwhile, popularity as a ranking metric demonstrates how much exposure the show has gotten and its outreach across as many demographics as possible, and is a ranking that is determined by the amount of users that rated the show regardless if it was positive or not.

@@

  It was found that the source material of the anime that it was adapted into had a significant impact on MAL viewership of anime, as shown with a linear regression model found in @sec-model. Additionally, the medium that the anime was adapted into also plays a factor in exposure, as TV shows and movies were shown to have many more MAL users viewing them. The format in how an anime is released also mattered, with shows that carry on over a specific seasonal period or in the format of a movie were shown to have the highest viewership. Finally, the year that an anime was released also plays a role in how popular an anime is on MAL, which is largely due to recency bias of users to watch and rate shows that tend to be newer.

@@

The important variable of note to consider from this list is `members`. This is a quantitative variable that popularity ranking on MAL is completely dependent on. The popularity ranking of an anime is directly affected by how many members an anime has, and so an anime that has the most members would have the #1 popularity ranking. The variables `type`, `source`, `episodes`, and `start_year` will be tested to see if they have any kind of influence on the amount of users that have specific shows on their lists.

@@

The format that the anime was presented in was shown to affect MAL viewership as demonstrated in @fig-membertype. Most notable, TV anime and movies demonstrated to have the highest amount of members attached to a given show within those formats. TV anime and movies are the most accessible formats to watch on streaming services such as Crunchyroll or Netflix, which is a large reason for anime released in those formats to gain more exposure. In comparison, a large majority of ONAs, OVAs, and specials are one-off releases of already established TV anime series, and are not always important to the story of the main anime. As such, many MAL users could reasonably skip watching anime in those formats, which is demonstrated in @fig-membertype.

The length of an anime has an effect on MAL viewership as demonstrated in @fig-memberepisode. Most anime run on a seasonal schedule that typically last over three months, commonly called a one-cour show. Some shows run on two-cours, which is six months of release. One-cour and two-cour shows are typically around 12-13 or 24-26 episodes respectively, and are the most common format to release a series. This isn't a definitive standard however, and there are anime that stray from this typical release schedule. However, those that do follow cour-based releases see much higher MAL viewership compared to other shows with differing episode lengths. There is a spike near the 1 episode mark, which is likely indicative of movies, which naturally are only 1 continuous episode. Similarly to how the movie and TV format impacts MAL viewership, there is a reflection of how specific an anime has to be released to garner more viewership from MAL users.

The source material of a show was demonstrated to have a significant impact in several adaptation mediums as outlined in @sec-model. However, @fig-membersource gives another perspective by visualizing the more popular source materials that turn into anime adaptations. Manga, which are Japanese-stylized comics, and light novels, which is a popular novel format with anime-stylized illustrations are demonstrated to have the highest viewership from MAL users. There are other novel formats that are present, such as visual novels which are stories contained within video games, and web novels which are stories only available to read online, but do not have as much exposure as light novels. Manga and light novels are the most popular mediums that anime adapt from which is reflected in @fig-membersource. Anime originals have an interesting observation in that they seem to demonstrate similar levels of popularity as manga and light novels, which may be related to how they are released. Anime originals tend to garner interest from MAL users as they have no baseline to assess the show or any preconceived opinions on them, which can at least encourage users to watch a few episodes to see if they enjoy it. If it was added to their list, even if they did not finish it, it counts towards popularity rankings on MAL. Regardless, the source material is an important aspect to consider as many people who watch anime also read the source material, meaning that there is already an initial interest in watching the show that can initially boost the anime's popularity and create more exposure for it to other users.

For the year or years that an anime was in broadcast for, there tended to be a continuous increase of viewership in anime titles around past 1975 as seen in @fig-memberyear. The anime medium as a whole evolved around this time with more and more titles being released as the years went by, so this observation was natural. However, something to consider is the advantage that newer anime have over older titles. Since MAL launched in 2004, new titles progressively were added to the database as they were released. Therefore, it should be noted that newer anime are more likely to be added to a user's list in comparison to older titles, as users can actively add titles to their list as the shows release. However, unless a user remembers older titles that they watch and actively add them to their lists, those titles would be added less often to user's lists, with newer anime being released every season that they would be watching as well.

@@

There are many limitations that are present in this statistical analysis. First, the depth of information is vast as there are many other variables that can be considered when determining the popularity of an anime. Factors from the production standpoint, such as the studios that produced the anime to licensors that release the show on platforms to be watched on are also important for garnering attention to shows. In addition, factors that may give more information about what the show might be about such as the genres and themes may also play an important role as personal appeaal to specific genres may help gravitate MAL users to watch particular shows.

Another consideration that has to be made is in regards to localization, which is closely related to the facet of licensing anime. Many anime are released in an English dubbed format or other language dub. However, this is not the standard, and many anime do not receive any kind of localization, and as such are either untranslated in other languages or have subtitles in a Japanese dub. This can affect MAL viewership considerably, as shows that are localized to some degree reach overseas demographics from Japan much easier and creating more exposure for those titles, which could not be analyzed in this report.

One final consideration that has to be made is how MAL users choose to use MAL as a service. As noted previously, many users can watch a show and put it on their list, but not rate it, causing inflated ratings for specific shows. This can also be applied to popularity rankings as well, as not all users in MAL are proactive in adding every single anime that they watch on their list. There is no functionality to link streaming services to MAL to record that a user has watched a show, and so finding the popularity of a show is also dependent on the user itself, and if they decide to put it on their list.

Overall, this report demonstrated aspects of a show that factors its exposure, and as such affect the total viewership from MAL users, which can reasonably extend past MAL users and be applied to any person that consumes anime. There are many areas which can be iterated on, however the overall impact from these factors are clearly seen, and should be taken into account by newer users to MAL or new anime watchers in general.
